Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-07-29 supplement.tex
expand details of populations used in supp

\small
\tableofcontents
\normalsize
\newpage

@@

\aprcomment{TODO: expand this section to include further discussion about why
we chose each population, and why we have omitted some (such as those suggested
in the reviews).}

>>>>

\small
\tableofcontents
\normalsize
%\newpage

@@

The number of publicly available whole-genome sequenced individuals from a
diverse set of African groups has grown in recent years
\citep[e.g.,][]{Mallick2016-lx,Bergstrom2020-cy,Schlebusch2020-zo}. Our choice
of populations was motivated by both technical and study design considerations.
First, while the diversity and linkage disequilibrium statistics used in our
inferences are robust to low coverage sequencing data \citep{Ragsdale2019-nt},
we wanted to have at least 20 individuals per population to increase accuracy
in statistical measurements by reducing the variance due to small sample sizes
\citep{Ragsdale2020-nz}. Second, merging of datasets post-variant calling can
introduce biases in demographic inference due to batch effects. We therefore
wanted to be able to perform joint calling in all of our samples. Together,
these considerations make the jointly called Thousand Genomes and ADRP dataset
best-suited for our demographic inference.

From a study design perspective, our choice of populations aimed to improve our
understanding of early human demography in Africa. The Nama derive ancestry
from a relatively deeply diverged population branch, and thus their demographic
history is of unique interest. Given previous archaeological and genetic
evidence, we expected that a minimal model for the Nama must include
pastoralist East African groups that contributed to the Nama
\citep[e.g.,][]{Uren2016-nn}, as well as recent European admixture, each of
which are represented in our jointly called dataset. Finally, because previous
studies have suggested a role for ``ghost'' archaic admixture or deep structure
in West African populations \citep[e.g.,][]{Speidel2019-nj,Durvasula2020-td},
and because these same sample sets are included in our dataset, we chose to
also include representatives of West African ancestry.
